---
title: "Canoe-Sprint-Body-Sequencing-mdown"
author: "Aaron Beach"
date: "22/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries

```{r, results='hide', message=FALSE}

library(data.table)
library(tictoc)
library(ggplot2)
library(plyr)
library(dplyr)
library(signal)
library(roll)
library(pracma)
library(plotly)
source("peakdet.R")
library(rootSolve)
library(scales)
library(tidyr)
library(qpcR)

library(DT)

```

Import data (shiny version uses input from ui)

```{r, results='hide',message=FALSE}
BoatdfAl <- data.frame(fread(choose.files(default = "C:/Users/aaron.beach/CaptureU", caption = "Select Boat File")))
PelvisdfAl <- data.frame(fread(choose.files(default = "C:/Users/aaron.beach/CaptureU", caption = "Select Pelvis File")))
ThoraxdfAl <- data.frame(fread(choose.files(default = "C:/Users/aaron.beach/CaptureU", caption = "Select Thorax File")))
MinimaxdfAl <- data.frame(fread(choose.files(default = "C:/Users/aaron.beach/CaptureU", caption = "Select Minimax File")))

```

Calculate Sample Rate, then trim data to between 60-90 seconds

```{r, results='hide',message=FALSE}

t = length(BoatdfAl$time_s)-1
SampleRateTS <- matrix(0, ncol = 1, nrow = t)
for (i in 1:t) {
  SampleRateTS[i,] <- 1/(BoatdfAl$time_s[i+1]-BoatdfAl$time_s[i])
}
SampleRate <- median(SampleRateTS)



start = SampleRate*60
end = SampleRate*90

BoatdfAl <- BoatdfAl[start:end,]
PelvisdfAl <- PelvisdfAl[start:end,]
ThoraxdfAl <- ThoraxdfAl[start:end,]
```

Reset the index/column V1 from zero

```{r, results='hide',message=FALSE}

row.names(BoatdfAl)<-1:nrow(BoatdfAl)
row.names(PelvisdfAl)<-1:nrow(PelvisdfAl)
row.names(ThoraxdfAl)<-1:nrow(ThoraxdfAl)

BoatdfAl$V1<-1:nrow(BoatdfAl)
PelvisdfAl$V1<-1:nrow(PelvisdfAl)
ThoraxdfAl$V1<-1:nrow(ThoraxdfAl)
```

Adjust values i.e. if using the aligned files, the gyro is converted to rad/s, so to convert back to deg/s multiply by 57.2958

The global angle data is adjusted based on the offset from the boat orientation during the static pose. Done manually but developing an auto way to do this.

```{r, results='hide',message=FALSE}
#PelvisdfAl$gx_deg.s = PelvisdfAl$gx_deg.s*57.2958
#ThoraxdfAl$gx_deg.s = ThoraxdfAl$gx_deg.s*57.2958
PelvisdfAl$z_deg2 = PelvisdfAl$z_deg-BoatdfAl$z_deg+10
ThoraxdfAl$z_deg2 = ThoraxdfAl$z_deg-BoatdfAl$z_deg+8

```

Create spectrum plots to identify filtering frequency.
Filter each variable using a butterworth filter.

```{r, results='hide',message=FALSE}
spectrum(BoatdfAl$"ax_m.s.s", method = "ar")


bf <- butter(4, 0.1, type="low")
BoatdfAl$AccFilt <- filtfilt(bf, BoatdfAl$"ax_m.s.s")


#spectrum(PelvisdfAl$"gx_deg.s", method = "ar")

bf <- butter(4, 0.1, type="low")
PelvisdfAl$gyroxfilt <- filtfilt(bf, PelvisdfAl$"gx_deg.s")

#spectrum(ThoraxdfAl$"gx_deg.s", method = "ar")

bf <- butter(4, 0.1, type="low")
ThoraxdfAl$gyroxfilt <- filtfilt(bf, ThoraxdfAl$"gx_deg.s")

#spectrum(PelvisdfAl$z_deg2, method = "ar")

bf <- butter(4, 0.1, type="low")
PelvisdfAl$z_degfilt <- filtfilt(bf, PelvisdfAl$z_deg2)

#spectrum(ThoraxdfAl$z_deg2, method = "ar")

bf <- butter(4, 0.1, type="low")
ThoraxdfAl$z_degfilt <- filtfilt(bf, ThoraxdfAl$z_deg2)
#spectrum(ThoraxdfAl$z_degfilt, method = "ar")


```

To split the data into strokes:

Identify acceleration peaks (Event)
Use the second column (first and 3rd column are the values for where the "mountain" starts and ends)
Check the plot to see if these were identified correctly, if not adjust findpeaks criteria

```{r, results='hide',message=FALSE}
Event <- findpeaks((BoatdfAl$AccFilt), minpeakheight = 1, minpeakdistance = 50)

ev <-  ggplot() + geom_line(aes(x=BoatdfAl$V1, y=(BoatdfAl$AccFilt))) + geom_point(aes(x=Event[,2], y=Event[,1]))
ggplotly(ev)


Event <- Event[,2]
Event <- sort(Event, decreasing = FALSE)

```

If the first peak doesn't have a zero value prior (due to where the data was trimmed), remove it.

```{r, results='hide',message=FALSE}
if(which.min(BoatdfAl$AccFilt[1:Event[1]]) >0){
  Event <- Event[-1]
}
```

Create stroke cycle start/end as the zero prior to a peak.

```{r, results='hide',message=FALSE}


zero <- NULL
cycle <- NULL
cycle[1] = tail((which(BoatdfAl$AccFilt[1:Event[1]] <0)), n=1)


for (r in 1:(length(Event))){
  t = r+1
  # framer = Event[r,2] - BoatdfAl$V1[1]
  # framet = Event[t,2] - BoatdfAl$V1[1]
  
  tryCatch((cycle[t] = tail((which(BoatdfAl$AccFilt[Event[r]:Event[t]] <0)), n=1) + Event[r]),error = function(e) print(NA))
}

```

Cut up data into stroke cycles, i.e. cycle 1:2, cycle 2:3 etc.

This code often throws up errors due to uneven rows, NAs etc. Not an issue in RStudio, but in RShiny the app stops. tryCatch ignores the error.

```{r, results='hide',message=FALSE}
BoatAcc = NULL
BoatAcc1 = NULL
BoatAcc2 = NULL
PelvisGyro = NULL
PelvisGyro1 = NULL
PelvisGyro2 = NULL
ThoraxGyro = NULL
ThoraxGyro1 = NULL
ThoraxGyro2 = NULL
PelvisRot = NULL
PelvisRot1 = NULL
PelvisRot2 = NULL
ThoraxRot = NULL
ThoraxRot1 = NULL
ThoraxRot2 = NULL

for (c in 1:(length(Event))){
  t = c+1
  tryCatch((BoatAcc[[c]] = BoatdfAl$AccFilt[cycle[c]:cycle[t]]), error = function(e) print(NA))
  tryCatch((PelvisGyro[[c]] = PelvisdfAl$gyroxfilt[cycle[c]:cycle[t]]),error = function(e) print(NA))
  tryCatch((ThoraxGyro[[c]] = ThoraxdfAl$gyroxfilt[cycle[c]:cycle[t]]),error = function(e) print(NA))
  tryCatch((PelvisRot[[c]] = PelvisdfAl$z_degfilt[cycle[c]:cycle[t]]),error = function(e) print(NA))
  tryCatch((ThoraxRot[[c]] = ThoraxdfAl$z_degfilt[cycle[c]:cycle[t]]),error = function(e) print(NA))
  
}
```


Use Thorax Gyro to determine if Left or Right is the first stroke.
If first stroke max is positive, then it is a Left Stroke.

```{r, results='hide',message=FALSE}
if (max(ThoraxRot[[1]]) >0){
  Side1 <- "Left"
  
}else{
  Side1 <- "Right"
  
}
```

Cut up variables per stroke.
Label Left and Right according to the above.

```{r, results='hide',message=FALSE}

for (i in seq(2,length(BoatAcc),2)){
  k = i-1
  tryCatch((BoatAcc2[[i-1]] = BoatAcc[[i]]), error = function(e) print(NA))
  tryCatch((BoatAcc1[[i-1]] = BoatAcc[[k]]), error = function(e) print(NA))
}

BoatAcc1 <- plyr::compact(BoatAcc1)
BoatAcc2 <- plyr::compact(BoatAcc2)

if (Side1 == "Left"){
  BoatAccLeft <- BoatAcc1
    BoatAccRight <- BoatAcc2
} else {
    BoatAccRight <- BoatAcc1
    BoatAccLeft <- BoatAcc2
}



for (i in seq(2,length(PelvisGyro),2)){
  k = i-1
  tryCatch((PelvisGyro2[[i-1]] = PelvisGyro[[i]]), error = function(e) print(NA))
  tryCatch((PelvisGyro1[[i-1]] = PelvisGyro[[k]]), error = function(e) print(NA))
}

PelvisGyro1 <- plyr::compact(PelvisGyro1)
PelvisGyro2 <- plyr::compact(PelvisGyro2)

if (Side1 == "Left"){
  PelvisGyroLeft <- PelvisGyro1
    PelvisGyroRight <- PelvisGyro2
} else {
    PelvisGyroRight <- PelvisGyro1
    PelvisGyroLeft <- PelvisGyro2
}

for (i in seq(2,length(ThoraxGyro),2)){
  k = i-1
  tryCatch((ThoraxGyro2[[i-1]] = ThoraxGyro[[i]]), error = function(e) print(NA))
  tryCatch((ThoraxGyro1[[i-1]] = ThoraxGyro[[k]]), error = function(e) print(NA))
}


ThoraxGyro1 <- plyr::compact(ThoraxGyro1)
ThoraxGyro2 <- plyr::compact(ThoraxGyro2)

if (Side1 == "Left"){
  ThoraxGyroLeft <- ThoraxGyro1
    ThoraxGyroRight <- ThoraxGyro2
} else {
    ThoraxGyroRight <- ThoraxGyro1
    ThoraxGyroLeft <- ThoraxGyro2
}

for (i in seq(2,length(PelvisRot),2)){
  k = i-1
  tryCatch((PelvisRot2[[i-1]] = PelvisRot[[i]]), error = function(e) print(NA))
  tryCatch((PelvisRot1[[i-1]] = PelvisRot[[k]]), error = function(e) print(NA))
}

PelvisRot1 <- plyr::compact(PelvisRot1)
PelvisRot2 <- plyr::compact(PelvisRot2)

if (Side1 == "Left"){
  PelvisRotLeft <- PelvisRot1
    PelvisRotRight <- PelvisRot2
} else {
    PelvisRotRight <- PelvisRot1
    PelvisRotLeft <- PelvisRot2
}

for (i in seq(2,length(ThoraxRot),2)){
  k = i-1
  tryCatch((ThoraxRot2[[i-1]] = ThoraxRot[[i]]), error = function(e) print(NA))
  tryCatch((ThoraxRot1[[i-1]] = ThoraxRot[[k]]), error = function(e) print(NA))
}

ThoraxRot1 <- plyr::compact(ThoraxRot1)
ThoraxRot2 <- plyr::compact(ThoraxRot2)

if (Side1 == "Left"){
  ThoraxRotLeft <- ThoraxRot1
    ThoraxRotRight <- ThoraxRot2
} else {
    ThoraxRotRight <- ThoraxRot1
    ThoraxRotLeft <- ThoraxRot2
}


```

Minimax data is 100Hz and not synced. So deal with it separately.
Divide into the same period of time, using time column (rather than row index).

```{r, results='hide',message=FALSE}

Minimaxdf2 <-  subset(MinimaxdfAl, `Time`>=60 & `Time`<=90)
```

Minimax has a column "stks" which identifies the start of each stroke, alternating 1 and 2, with blanks in between (imported as NA).

```{r, results='hide',message=FALSE}
stks1 = which(Minimaxdf2$Stk == 1)
stks2 = which(Minimaxdf2$Stk == 2)
stks = c(stks1, stks2)
stks = sort(stks)
```

Cut up the Minimax Velocity column per Stroke.

```{r, results='hide',message=FALSE}
MinimaxdfVelocity = NULL
for (i in 2:length(stks)){
  k = i-1
  
  MinimaxdfVelocity[[k]] = Minimaxdf2[stks[k]:stks[i],"VAcc"]
  
}

MinimaxdfVelocity1=NULL
MinimaxdfVelocity2=NULL

for (i in seq(2,length(MinimaxdfVelocity),2)){
  k = i-1
  tryCatch((MinimaxdfVelocity2[[i-1]] = MinimaxdfVelocity[[i]]), error = function(e) print(NA))
  tryCatch((MinimaxdfVelocity1[[i-1]] = MinimaxdfVelocity[[k]]), error = function(e) print(NA))
  }

MinimaxdfVelocity1 <- plyr::compact(MinimaxdfVelocity1)
MinimaxdfVelocity2 <- plyr::compact(MinimaxdfVelocity2)
```

In a similar process to above, whether the first stroke is a left or right is determined by the Minimax Roll column.
If the peak roll for the first stroke is positive, then the first stroke is Right.

```{r, results='hide',message=FALSE}
MinimaxdfRoll = NULL
for (i in 2:length(stks)){
  k = i-1
  MinimaxdfRoll[[k]] = Minimaxdf2[stks[k]:stks[i],"Roll"]
  
}


if (max(MinimaxdfRoll[[1]]) >2){
  side = "right"
  MinimaxdfVelocityRight <- MinimaxdfVelocity1
  MinimaxdfVelocityLeft <- MinimaxdfVelocity2
  
}else{
  side = "left"
  MinimaxdfVelocityLeft <- MinimaxdfVelocity1
  MinimaxdfVelocityRight <- MinimaxdfVelocity2
  
}

MinimaxdfVelocityRight <- plyr::compact(MinimaxdfVelocity1)
MinimaxdfVelocityLeft <- plyr::compact(MinimaxdfVelocity2)
```

This process is common for all variables, normalising each stroke with varying data points, into a 0-100% scale.

```{r, results='hide', message=FALSE}

MinimaxdfVelocityRightNorm = NULL
for (i in 1:length(MinimaxdfVelocityRight)){
  xvalues = 1:length(MinimaxdfVelocityRight[[i]])
  yvalues = MinimaxdfVelocityRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  MinimaxdfVelocityRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

MinimaxdfVelocityLeftNorm = NULL
for (i in 1:length(MinimaxdfVelocityLeft)){
  xvalues = 1:length(MinimaxdfVelocityLeft[[i]])
  yvalues = MinimaxdfVelocityLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  MinimaxdfVelocityLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}
```

Mean, Standard deviation, positive and negative error bars, and max (magnitude and %Stroke) are also calculated.

```{r, results='hide', message=FALSE}

MinimaxdfVelocityRightNormCombined = do.call(cbind, MinimaxdfVelocityRightNorm)
MinimaxdfVelocityRightNormMean = rowMeans(MinimaxdfVelocityRightNormCombined)
MinimaxdfVelocityRightNormSD = apply(MinimaxdfVelocityRightNormCombined[,-1], 1, sd)
MinimaxdfVelocityRightNormPEB = MinimaxdfVelocityRightNormMean + MinimaxdfVelocityRightNormSD
MinimaxdfVelocityRightNormNEB = MinimaxdfVelocityRightNormMean - MinimaxdfVelocityRightNormSD

MinimaxdfVelocityRightNormCombined2 = as.data.frame(MinimaxdfVelocityRightNormCombined)
MinimaxdfVelocityRightNormCombined2$perc = c(0:100)
MinimaxdfVelocityRightNormCombined2 <- melt(MinimaxdfVelocityRightNormCombined2, id.vars="perc")

MinimaxdfVelocityRightNormMeanMax <- round(max(MinimaxdfVelocityRightNormMean),2)
MinimaxdfVelocityRightNormMeanMaxPC <- which.max(MinimaxdfVelocityRightNormMean)-1
```

All strokes are plotted together.

```{r, message=FALSE}

#output$MinimaxVelRight<- renderPlotly({
  
  fig <- plot_ly(MinimaxdfVelocityRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Minimax Velocity (m/s)"))
```

```{r, message=FALSE}
  fig
#})
```
 Process is repeated on the left side

```{r, include=FALSE,message=FALSE}

MinimaxdfVelocityLeftNormCombined = do.call(cbind, MinimaxdfVelocityLeftNorm)
MinimaxdfVelocityLeftNormMean = rowMeans(MinimaxdfVelocityLeftNormCombined)
MinimaxdfVelocityLeftNormSD = apply(MinimaxdfVelocityLeftNormCombined[,-1], 1, sd)
MinimaxdfVelocityLeftNormPEB = MinimaxdfVelocityLeftNormMean + MinimaxdfVelocityLeftNormSD
MinimaxdfVelocityLeftNormNEB = MinimaxdfVelocityLeftNormMean - MinimaxdfVelocityLeftNormSD

MinimaxdfVelocityLeftNormCombined2 = as.data.frame(MinimaxdfVelocityLeftNormCombined)
MinimaxdfVelocityLeftNormCombined2$perc = c(0:100)
MinimaxdfVelocityLeftNormCombined2 <- melt(MinimaxdfVelocityLeftNormCombined2, id.vars="perc")


MinimaxdfVelocityLeftNormMeanMax <- round(max(MinimaxdfVelocityLeftNormMean),2)
MinimaxdfVelocityLeftNormMeanMaxPC <- which.max(MinimaxdfVelocityLeftNormMean)-1

#output$MinimaxVelLeft<- renderPlotly({
  
  fig <- plot_ly(MinimaxdfVelocityLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Minimax Velocity (m/s)"))
  
  fig
#})

```

Both left and right mean and error bars are plotted together.

```{r, message=FALSE}
#output$MinimaxVelCombined<- renderPlotly({
  
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = MinimaxdfVelocityRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Minimax Velocity (m/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.9)) %>%
    config(displayModeBar = F)
  
  
  fig
  #})

```

The same process is repeated for the Boat Acceleration.

```{r, include=FALSE,message=FALSE}
#Boat normalised and plot

BoatAccRightNorm = NULL

for (i in 1:length(BoatAccRight)){
  xvalues = 1:length(BoatAccRight[[i]])
  yvalues = BoatAccRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  BoatAccRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}



BoatAccRightNormCombined = do.call(cbind, BoatAccRightNorm)
BoatAccRightNormMean = rowMeans(BoatAccRightNormCombined)
BoatAccRightNormSD = apply(BoatAccRightNormCombined[,-1], 1, sd)
BoatAccRightNormPEB = BoatAccRightNormMean + BoatAccRightNormSD
BoatAccRightNormNEB = BoatAccRightNormMean - BoatAccRightNormSD

BoatAccRightNormCombined2 = as.data.frame(BoatAccRightNormCombined)
BoatAccRightNormCombined2$perc = c(0:100)
BoatAccRightNormCombined2 <- melt(BoatAccRightNormCombined2, id.vars="perc")

BoatAccRightNormMeanSD = cbind.data.frame(BoatAccRightNormMean,BoatAccRightNormPEB,BoatAccRightNormNEB)

BoatAccRightNormMeanMax <- round(max(BoatAccRightNormMean),2)
BoatAccRightNormMeanMaxPC <- which.max(BoatAccRightNormMean)-1

#output$BoatAccRight<- renderPlotly({
  
  fig <- plot_ly(BoatAccRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Boat Acceleration (m/s/s)"))
  
  fig
#})






#BoatAccRightNormMeanSD <-  BoatAccRightNormMeanSD

# outputBoatAccRightMean<- renderPlotly({
#   
#   q <- ggplot(BoatAccRightNormMeanSD) + geom_line(aes(c(0:100),BoatAccRightNormMean))+ geom_line(aes(c(0:100),BoatAccRightNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),BoatAccRightNormNEB),linetype = "dashed")
#   scale_x_continuous(name="% of stroke")+
#     scale_y_continuous(name="Boat Acceleration (m/s/s)")
#   ggplotly(q)
# })


####################################
#Boat normalised and plot

BoatAccLeftNorm = NULL

for (i in 1:length(BoatAccLeft)){
  xvalues = 1:length(BoatAccLeft[[i]])
  yvalues = BoatAccLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  BoatAccLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}



BoatAccLeftNormCombined = do.call(cbind, BoatAccLeftNorm)
BoatAccLeftNormMean = rowMeans(BoatAccLeftNormCombined)
BoatAccLeftNormSD = apply(BoatAccLeftNormCombined[,-1], 1, sd)
BoatAccLeftNormPEB = BoatAccLeftNormMean + BoatAccLeftNormSD
BoatAccLeftNormNEB = BoatAccLeftNormMean - BoatAccLeftNormSD

BoatAccLeftNormCombined2 = as.data.frame(BoatAccLeftNormCombined)
BoatAccLeftNormCombined2$perc = c(0:100)
BoatAccLeftNormCombined2 <- melt(BoatAccLeftNormCombined2, id.vars="perc")

BoatAccLeftNormMeanSD = cbind.data.frame(BoatAccLeftNormMean,BoatAccLeftNormPEB,BoatAccLeftNormNEB)

BoatAccLeftNormMeanMax <- round(max(BoatAccLeftNormMean),2)
BoatAccLeftNormMeanMaxPC <- which.max(BoatAccLeftNormMean)-1

#output$BoatAccLeft<- renderPlotly({
  
  fig <- plot_ly(BoatAccLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Boat Acceleration (m/s/s)"))
  
  fig
#})
#BoatAccLeftNormMeanSD <-  BoatAccLeftNormMeanSD


#######################


#output$BoatAccCombined<- renderPlotly({
  
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = BoatAccRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Boat Acceleration')%>% 
    add_trace(y = BoatAccRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Boat Acceleration')%>% 
    add_trace(y = BoatAccLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Boat Acceleration (m/s/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.9)) %>%
    config(displayModeBar = F)
  
```
``` {r, message=FALSE}
  fig
  
#})
```

Pelvis Gyro (Rotational Velocity)

```{r, include=FALSE,message=FALSE}

PelvisGyroRightNorm = NULL
for (i in 1:length(PelvisGyroRight)){
  xvalues = 1:length(PelvisGyroRight[[i]])
  yvalues = PelvisGyroRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  PelvisGyroRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}


PelvisGyroRightNormCombined = do.call(cbind, PelvisGyroRightNorm)
PelvisGyroRightNormMean = (rowMeans(PelvisGyroRightNormCombined))
PelvisGyroRightNormSD = (apply(PelvisGyroRightNormCombined[,-1], 1, sd))
PelvisGyroRightNormPEB = (PelvisGyroRightNormMean + PelvisGyroRightNormSD)
PelvisGyroRightNormNEB = (PelvisGyroRightNormMean - PelvisGyroRightNormSD)

if (PelvisGyroRightNormMean[1] > 0){
  sign = 1
}else{
  sign = -1
}

PelvisGyroRightNormMean <- PelvisGyroRightNormMean*sign
PelvisGyroRightNormSD <-  PelvisGyroRightNormSD*sign
PelvisGyroRightNormPEB <-  PelvisGyroRightNormPEB*sign
PelvisGyroRightNormNEB <-  PelvisGyroRightNormNEB*sign


PelvisGyroRightNormCombined2 = (as.data.frame(PelvisGyroRightNormCombined))*sign
PelvisGyroRightNormCombined2$perc = c(0:100)
PelvisGyroRightNormCombined2 <- melt(PelvisGyroRightNormCombined2, id.vars="perc")

PelvisGyroRightNormMeanSD = cbind.data.frame(PelvisGyroRightNormMean,PelvisGyroRightNormPEB,PelvisGyroRightNormNEB)

PelvisGyroRightNormMeanMax <- round(max(PelvisGyroRightNormMean),2)
PelvisGyroRightNormMeanMaxPC <- which.max(PelvisGyroRightNormMean)-1

#output$PelvisGyroRight<- renderPlotly({
  
  fig <- plot_ly(PelvisGyroRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Velocity (deg/s)"))
  
  fig
  
#})


# output$PelvisGyroRightMean<- renderPlotly({
#   
#   q <-  ggplot(PelvisGyroRightNormMeanSD) + geom_line(aes(c(0:100),PelvisGyroRightNormMean))+ geom_line(aes(c(0:100),PelvisGyroRightNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),PelvisGyroRightNormNEB),linetype = "dashed")+
#     scale_x_continuous(name="% of stroke")+
#     scale_y_continuous(name="Rotation Velocity (deg/s)")
#   ggplotly(q)
# })



##########################
PelvisGyroLeftNorm = NULL
for (i in 1:length(PelvisGyroLeft)){
  xvalues = 1:length(PelvisGyroLeft[[i]])
  yvalues = PelvisGyroLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  PelvisGyroLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}


PelvisGyroLeftNormCombined = do.call(cbind, PelvisGyroLeftNorm)
PelvisGyroLeftNormMean = (rowMeans(PelvisGyroLeftNormCombined))
PelvisGyroLeftNormSD = (apply(PelvisGyroLeftNormCombined[,-1], 1, sd))
PelvisGyroLeftNormPEB = (PelvisGyroLeftNormMean + PelvisGyroLeftNormSD)
PelvisGyroLeftNormNEB = (PelvisGyroLeftNormMean - PelvisGyroLeftNormSD)

if (PelvisGyroLeftNormMean[1] > 0){
  sign = 1
}else{
  sign = -1
}

PelvisGyroLeftNormMean <- PelvisGyroLeftNormMean*sign
PelvisGyroLeftNormSD <-  PelvisGyroLeftNormSD*sign
PelvisGyroLeftNormPEB <-  PelvisGyroLeftNormPEB*sign
PelvisGyroLeftNormNEB <-  PelvisGyroLeftNormNEB*sign


PelvisGyroLeftNormCombined2 = (as.data.frame(PelvisGyroLeftNormCombined))*sign
PelvisGyroLeftNormCombined2$perc = c(0:100)
PelvisGyroLeftNormCombined2 <- melt(PelvisGyroLeftNormCombined2, id.vars="perc")

PelvisGyroLeftNormMeanMax <- round(max(PelvisGyroLeftNormMean),2)
PelvisGyroLeftNormMeanMaxPC <- which.max(PelvisGyroLeftNormMean)-1

#output$PelvisGyroLeft<- renderPlotly({
  
  fig <- plot_ly(PelvisGyroLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Velocity (deg/s)"))
  
  fig
#})

# output$PelvisGyroLeftMean<- renderPlotly({
#   
#   q <-  ggplot(PelvisGyroLeftNormMeanSD) + geom_line(aes(c(0:100),PelvisGyroLeftNormMean))+ geom_line(aes(c(0:100),PelvisGyroLeftNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),PelvisGyroLeftNormNEB),linetype = "dashed")+
#     scale_x_continuous(name="% of stroke")+
#     scale_y_continuous(name="Rotation Velocity (deg/s)")
#   ggplotly(q)
# })

#output$PelvisGyroCombined<- renderPlotly({
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = PelvisGyroRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Pelvis Rotation')%>% 
    add_trace(y = PelvisGyroRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Pelvis Rotation')%>% 
    add_trace(y = PelvisGyroLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Velocity (m/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.9)) %>%
    config(displayModeBar = F)
  
```

```{r, message=FALSE}
  fig
  
  
  
  
#})
```

Thorax Gyro (Rotational Velocity)

```{r, include=FALSE,message=FALSE}

ThoraxGyroRightNorm = NULL
for (i in 1:length(ThoraxGyroRight)){
  xvalues = 1:length(ThoraxGyroRight[[i]])
  yvalues = ThoraxGyroRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  ThoraxGyroRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

ThoraxGyroRightNormCombined = do.call(cbind, ThoraxGyroRightNorm)

ThoraxGyroRightNormMean = (rowMeans(ThoraxGyroRightNormCombined))
ThoraxGyroRightNormSD = (apply(ThoraxGyroRightNormCombined[,-1], 1, sd))
ThoraxGyroRightNormPEB = (ThoraxGyroRightNormMean + ThoraxGyroRightNormSD)
ThoraxGyroRightNormNEB = (ThoraxGyroRightNormMean - ThoraxGyroRightNormSD)

if (ThoraxGyroRightNormMean[1] > 0){
  sign = 1
}else{
  sign = -1
}

ThoraxGyroRightNormMean <- ThoraxGyroRightNormMean*sign
ThoraxGyroRightNormSD <-  ThoraxGyroRightNormSD*sign
ThoraxGyroRightNormPEB <-  ThoraxGyroRightNormPEB*sign
ThoraxGyroRightNormNEB <-  ThoraxGyroRightNormNEB*sign


ThoraxGyroRightNormCombined2 = (as.data.frame(ThoraxGyroRightNormCombined))*sign
ThoraxGyroRightNormCombined2$perc = c(0:100)
ThoraxGyroRightNormCombined2 <- melt(ThoraxGyroRightNormCombined2, id.vars="perc")

ThoraxGyroRightNormMeanMax <- round(max(ThoraxGyroRightNormMean),2)
ThoraxGyroRightNormMeanMaxPC <- which.max(ThoraxGyroRightNormMean)-1


#output$ThoraxGyroRight<- renderPlotly({
  
  
  fig <- plot_ly(ThoraxGyroRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Velocity (deg/s)"))
  
  fig
#})


# ThoraxGyroRightNormMeanSD = cbind.data.frame(ThoraxGyroRightNormMean,ThoraxGyroRightNormPEB,ThoraxGyroRightNormNEB)
# output$ThoraxGyroRightMean<- renderPlotly({
#   q <-  ggplot(ThoraxGyroRightNormMeanSD) + geom_line(aes(c(0:100),ThoraxGyroRightNormMean))+ geom_line(aes(c(0:100),ThoraxGyroRightNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),ThoraxGyroRightNormNEB),linetype = "dashed")+
#     scale_x_continuous(name="% of stroke")+
#     scale_y_continuous(name="Rotation Velocity (deg/s)")
#   ggplotly(q)
#   
#   
# })


##########################################

ThoraxGyroLeftNorm = NULL
for (i in 1:length(ThoraxGyroLeft)){
  xvalues = 1:length(ThoraxGyroLeft[[i]])
  yvalues = ThoraxGyroLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  ThoraxGyroLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

ThoraxGyroLeftNormCombined = do.call(cbind, ThoraxGyroLeftNorm)

ThoraxGyroLeftNormMean = (rowMeans(ThoraxGyroLeftNormCombined))
ThoraxGyroLeftNormSD = (apply(ThoraxGyroLeftNormCombined[,-1], 1, sd))
ThoraxGyroLeftNormPEB = (ThoraxGyroLeftNormMean + ThoraxGyroLeftNormSD)
ThoraxGyroLeftNormNEB = (ThoraxGyroLeftNormMean - ThoraxGyroLeftNormSD)

if (ThoraxGyroLeftNormMean[1] > 0){
  sign = 1
}else{
  sign = -1
}

ThoraxGyroLeftNormMean <- ThoraxGyroLeftNormMean*sign
ThoraxGyroLeftNormSD <-  ThoraxGyroLeftNormSD*sign
ThoraxGyroLeftNormPEB <-  ThoraxGyroLeftNormPEB*sign
ThoraxGyroLeftNormNEB <-  ThoraxGyroLeftNormNEB*sign


ThoraxGyroLeftNormCombined2 = (as.data.frame(ThoraxGyroLeftNormCombined))*sign
ThoraxGyroLeftNormCombined2$perc = c(0:100)
ThoraxGyroLeftNormCombined2 <- melt(ThoraxGyroLeftNormCombined2, id.vars="perc")

ThoraxGyroLeftNormMeanMax <- round(max(ThoraxGyroLeftNormMean),2)
ThoraxGyroLeftNormMeanMaxPC <- which.max(ThoraxGyroLeftNormMean)-1


#output$ThoraxGyroLeft<- renderPlotly({
  
  fig <- plot_ly(ThoraxGyroLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Velocity (deg/s)"))
  
  fig
#})


# ThoraxGyroLeftNormMeanSD = cbind.data.frame(ThoraxGyroLeftNormMean,ThoraxGyroLeftNormPEB,ThoraxGyroLeftNormNEB)
# output$ThoraxGyroLeftMean<- renderPlotly({
#   q <-  ggplot(ThoraxGyroLeftNormMeanSD) + geom_line(aes(c(0:100),ThoraxGyroLeftNormMean))+ geom_line(aes(c(0:100),ThoraxGyroLeftNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),ThoraxGyroLeftNormNEB),linetype = "dashed")+
#     scale_x_continuous(name="% of stroke")+
#     scale_y_continuous(name="Rotation Velocity (deg/s)")
#   ggplotly(q)
#   
#   
# })

#output$ThoraxGyroCombined<- renderPlotly({
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = ThoraxGyroRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Thorax Rotation')%>% 
    add_trace(y = ThoraxGyroRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Thorax Rotation')%>% 
    add_trace(y = ThoraxGyroLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Velocity (m/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.9)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
#})
```

All means are plotted together for the right side

```{r, include=FALSE,message=FALSE}
#output$SequenceRight<- renderPlotly({
  
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = BoatAccRightNormMean*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              line = list(color = 'black', dash = 'dot'),
              showlegend = TRUE, name = 'Boat Acceleration')%>% 
    add_trace(y = BoatAccRightNormPEB*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccRightNormNEB*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityRightNormMean, type = 'scatter', mode = 'lines',yaxis = "y2",
              line = list(color = 'rgba(122, 39, 160, 1)', dash = 'dot'),
              showlegend = TRUE, name = 'Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityRightNormPEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160, 0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityRightNormNEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroRightNormMean, type = 'scatter', mode = 'lines', line = list(color = 'rgba(21, 0, 250, 1)'),
              showlegend = TRUE, name = 'Thorax Rotation')%>% 
    add_trace(y = ThoraxGyroRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroRightNormMean, type = 'scatter', mode = 'lines',line = list(color = 'rgba(255, 117, 31,1)'),
              showlegend = TRUE, name = 'Pelvis Rotation')%>% 
    add_trace(y = PelvisGyroRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Velocity (m/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE,
                                 range = c(-50,200)
                    ),
                    yaxis2 = list(title = "Velocity (m/s)",
                                  overlaying = "y",
                                  side = "right",
                                  showgrid = FALSE,
                                  showline = FALSE,
                                  showticklabels = TRUE,
                                  ticks = 'outside',
                                  zeroline = TRUE,
                                  range = c(3,4),
                                  color = 'rgba(122, 39, 160, 1)'),
                    margin = list(l = 0, r = 50, b = 0, t = 0),
                    legend = list(orientation = 'h', x =0, y = -0.2)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
  
  
  
  
#})
```
  
And Left side.

```{r, include=FALSE,message=FALSE}
#output$SequenceLeft<- renderPlotly({
  
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = BoatAccLeftNormMean*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              line = list(color = 'black',dash = 'dot'),
              showlegend = TRUE, name = 'Boat Acceleration')%>% 
    add_trace(y = BoatAccLeftNormPEB*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccLeftNormNEB*50, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormMean, type = 'scatter', mode = 'lines',yaxis = "y2",
              line = list(color = 'rgba(122, 39, 160, 1)',dash = 'dot'),
              showlegend = TRUE, name = 'Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormPEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160, 0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormNEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'rgba(21, 0, 250, 1)'),
              showlegend = TRUE, name = 'Thorax Rotation')%>% 
    add_trace(y = ThoraxGyroLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxGyroLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroLeftNormMean, type = 'scatter', mode = 'lines',line = list(color = 'rgba(255, 117, 31,1)'),
              showlegend = TRUE, name = 'Pelvis Rotation')%>% 
    add_trace(y = PelvisGyroLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisGyroLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Velocity (m/s)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE,
                                 range = c(-50,200)),
                    yaxis2 = list(title = "Stroke Rate (spm)",
                                  overlaying = "y",
                                  side = "right",
                                  showgrid = FALSE,
                                  showline = FALSE,
                                  showticklabels = TRUE,
                                  ticks = 'outside',
                                  zeroline = FALSE,
                                  range = c(3,4),
                                  color = 'rgba(122, 39, 160, 1)'),
                    margin = list(l = 0, r = 50, b = 0, t = 0),
                    legend = list(orientation = 'h', x =0, y = -0.2)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
#})
```

Max values are collated into a datatable.

```{r,message=FALSE}
SequencedataRight <- data.frame(MinimaxdfVelocityRightNormMeanMax, MinimaxdfVelocityRightNormMeanMaxPC, PelvisGyroRightNormMeanMax,  PelvisGyroRightNormMeanMaxPC, ThoraxGyroRightNormMeanMax, ThoraxGyroRightNormMeanMaxPC)
colnames(SequencedataRight) <- c("Minimax Velocity Max (m/s)", "%", "Pelvis Rotation Velocity Max (deg/s)",  "%", "Thorax Rotation Velocity Max (deg/s)", "%")
SequencedataLeft <- data.frame(MinimaxdfVelocityLeftNormMeanMax, MinimaxdfVelocityLeftNormMeanMaxPC, PelvisGyroLeftNormMeanMax,  PelvisGyroLeftNormMeanMaxPC, ThoraxGyroLeftNormMeanMax, ThoraxGyroLeftNormMeanMaxPC)
colnames(SequencedataLeft) <- c("Minimax Velocity Max (m/s)", "%", "Pelvis Rotation Velocity Max (deg/s)",  "%", "Thorax Rotation Velocity Max (deg/s)", "%")

Sequencedata <- rbind(SequencedataRight,SequencedataLeft)


#output$table_VelSequence <- renderDataTable({ 
  
  
  datatable(Sequencedata,  rownames = c("Right", "Left"), options = list(columnDefs = list(list(className = 'dt-center', targets = "_all")),dom='t', ordering=F))%>% formatStyle(
    columns = c(3,4),
    #c('250m splits (secs)', "Race 2", "Avg Velocity (m/s)", "Avg Prog Speed (%)"),
    valueColumns = 0,
    target = 'cell',
    backgroundColor = 'rgba(112, 165, 255, 1)')
#})
  
```


Repeat for Pelvis orientation (global angle)
```{r, include=FALSE,message=FALSE}


PelvisRotRightNorm = NULL
for (i in 1:length(PelvisRotRight)){
  xvalues = 1:length(PelvisRotRight[[i]])
  yvalues = PelvisRotRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  PelvisRotRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

PelvisRotRightNormCombined = do.call(cbind, PelvisRotRightNorm)
PelvisRotRightNormMean = rowMeans(PelvisRotRightNormCombined)
PelvisRotRightNormSD = apply(PelvisRotRightNormCombined[,-1], 1, sd)
PelvisRotRightNormPEB = PelvisRotRightNormMean + PelvisRotRightNormSD
PelvisRotRightNormNEB = PelvisRotRightNormMean - PelvisRotRightNormSD

if (PelvisRotRightNormMean[1] < 0){
  sign = 1
}else{
  sign = -1
}


PelvisRotRightNormMean <- PelvisRotRightNormMean*sign
PelvisRotRightNormSD <-  PelvisRotRightNormSD*sign
PelvisRotRightNormPEB <-  PelvisRotRightNormPEB*sign
PelvisRotRightNormNEB <-  PelvisRotRightNormNEB*sign


PelvisRotRightNormCombined2 = (as.data.frame(PelvisRotRightNormCombined))*sign
PelvisRotRightNormCombined2$perc = c(0:100)
PelvisRotRightNormCombined2 <- melt(PelvisRotRightNormCombined2, id.vars="perc")

PelvisRotRightNormMeanMax <- round(max(PelvisRotRightNormMean),2)
PelvisRotRightNormMeanMaxPC <- which.max(PelvisRotRightNormMean)-1


# ggplot(PelvisRotRightNormCombined2) + geom_line(aes(perc,value, colour = variable))+ theme(legend.position = "none")
# 
# 
# ggplot(PelvisRotRightNormMeanSD) + geom_line(aes(c(0:100),PelvisRotRightNormMean))+ geom_line(aes(c(0:100),PelvisRotRightNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),PelvisRotRightNormNEB),linetype = "dashed")

#output$PelvisRotRight<- renderPlotly({
  
  fig <- plot_ly(PelvisRotRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Angle (deg)"))
  
  fig
  
#})


###NORMALISE PELVIS LEFT ORIENTATION DATA AND PLOT #############



PelvisRotLeftNorm = NULL
for (i in 1:length(PelvisRotLeft)){
  xvalues = 1:length(PelvisRotLeft[[i]])
  yvalues = PelvisRotLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  PelvisRotLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

PelvisRotLeftNormCombined = do.call(cbind, PelvisRotLeftNorm)
PelvisRotLeftNormMean = rowMeans(PelvisRotLeftNormCombined)
PelvisRotLeftNormSD = apply(PelvisRotLeftNormCombined[,-1], 1, sd)
PelvisRotLeftNormPEB = PelvisRotLeftNormMean + PelvisRotLeftNormSD
PelvisRotLeftNormNEB = PelvisRotLeftNormMean - PelvisRotLeftNormSD

if (PelvisRotLeftNormMean[1] < 0){
  sign = 1
}else{
  sign = -1
}

PelvisRotLeftNormMean <- PelvisRotLeftNormMean*sign
PelvisRotLeftNormSD <-  PelvisRotLeftNormSD*sign
PelvisRotLeftNormPEB <-  PelvisRotLeftNormPEB*sign
PelvisRotLeftNormNEB <-  PelvisRotLeftNormNEB*sign

PelvisRotLeftNormCombined2 = (as.data.frame(PelvisRotLeftNormCombined))*sign
PelvisRotLeftNormCombined2$perc = c(0:100)
PelvisRotLeftNormCombined2 <- melt(PelvisRotLeftNormCombined2, id.vars="perc")

PelvisRotLeftNormMeanMax <- round(max(PelvisRotLeftNormMean),2)
PelvisRotLeftNormMeanMaxPC <- which.max(PelvisRotLeftNormMean)-1 

# ggplot(PelvisRotLeftNormCombined2) + geom_line(aes(perc,value, colour = variable))+ theme(legend.position = "none")+
#   scale_y_reverse()
# 
# 
# ggplot(PelvisRotLeftNormMeanSD) + geom_line(aes(c(0:100),PelvisRotLeftNormMean))+ geom_line(aes(c(0:100),PelvisRotLeftNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),PelvisRotLeftNormNEB),linetype = "dashed") +
#   scale_y_reverse()






#output$PelvisRotLeft<- renderPlotly({
  
  fig <- plot_ly(PelvisRotLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Angle (deg)"))
  
  fig
  
#})
  

#output$PelvisRotCombined<- renderPlotly({
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = PelvisRotRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Pelvis Rotation')%>% 
    add_trace(y = PelvisRotRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Pelvis Rotation')%>% 
    add_trace(y = PelvisRotLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Angle (deg)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.2)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
  
  
  
  
#})
  
```


And Thorax orientation (global angle)
```{r, include=FALSE,message=FALSE}

###NORMALISE THORAX ORIENTATION DATA AND PLOT #############

# ThoraxRotNorm = NULL
# for (i in 1:length(ThoraxRot)){
#   xvalues = 1:length(ThoraxRot[[i]])
#   yvalues = ThoraxRot[[i]]
#   output_x_vals <- seq(1,length(xvalues),length.out=101)
#   #
#   # compute the interpolated values; this would be done for each input time series
#   #
#   #interp_output[[,i]]<- 
#   
#   ThoraxRotNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
# }
# 
# ThoraxRotNormCombined = do.call(cbind, ThoraxRotNorm)
# ThoraxRotNormMean = rowMeans(ThoraxRotNormCombined)
# ThoraxRotNormSD = apply(ThoraxRotNormCombined[,-1], 1, sd)
# ThoraxRotNormPEB = ThoraxRotNormMean + ThoraxRotNormSD
# ThoraxRotNormNEB = ThoraxRotNormMean - ThoraxRotNormSD
# 
# ThoraxRotNormCombined2 = as.data.frame(ThoraxRotNormCombined)
# ThoraxRotNormCombined2$perc = c(0:100)
# ThoraxRotNormCombined2 <- melt(ThoraxRotNormCombined2, id.vars="perc")
# ThoraxRotNormMeanSD = cbind.data.frame(ThoraxRotNormMean,ThoraxRotNormPEB,ThoraxRotNormNEB)


# ggplot(ThoraxRotNormCombined2) + geom_line(aes(perc,value, colour = variable))+ theme(legend.position = "none")
# 
# 
# ggplot(ThoraxRotNormMeanSD) + geom_line(aes(c(0:100),ThoraxRotNormMean))+ geom_line(aes(c(0:100),ThoraxRotNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),ThoraxRotNormNEB),linetype = "dashed")


###NORMALISE THORAX RIGHT ORIENTATION DATA AND PLOT #############

ThoraxRotRightNorm = NULL
for (i in 1:length(ThoraxRotRight)){
  xvalues = 1:length(ThoraxRotRight[[i]])
  yvalues = ThoraxRotRight[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  ThoraxRotRightNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

ThoraxRotRightNormCombined = do.call(cbind, ThoraxRotRightNorm)
ThoraxRotRightNormMean = rowMeans(ThoraxRotRightNormCombined)
ThoraxRotRightNormSD = apply(ThoraxRotRightNormCombined[,-1], 1, sd)
ThoraxRotRightNormPEB = ThoraxRotRightNormMean + ThoraxRotRightNormSD
ThoraxRotRightNormNEB = ThoraxRotRightNormMean - ThoraxRotRightNormSD

if (ThoraxRotRightNormMean[1] < 0){
  sign = 1
}else{
  sign = -1
}

ThoraxRotRightNormMean <- ThoraxRotRightNormMean*sign
ThoraxRotRightNormSD <-  ThoraxRotRightNormSD*sign
ThoraxRotRightNormPEB <-  ThoraxRotRightNormPEB*sign
ThoraxRotRightNormNEB <-  ThoraxRotRightNormNEB*sign

ThoraxRotRightNormCombined2 = (as.data.frame(ThoraxRotRightNormCombined))*sign
ThoraxRotRightNormCombined2$perc = c(0:100)
ThoraxRotRightNormCombined2 <- melt(ThoraxRotRightNormCombined2, id.vars="perc")

ThoraxRotRightNormMeanMax <- round(max(ThoraxRotRightNormMean),2)
ThoraxRotRightNormMeanMaxPC <- which.max(ThoraxRotRightNormMean)-1 

# ggplot(ThoraxRotRightNormCombined2) + geom_line(aes(perc,value, colour = variable))+ theme(legend.position = "none")
# 
# 
# ggplot(ThoraxRotRightNormMeanSD) + geom_line(aes(c(0:100),ThoraxRotRightNormMean))+ geom_line(aes(c(0:100),ThoraxRotRightNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),ThoraxRotRightNormNEB),linetype = "dashed")


#output$ThoraxRotRight<- renderPlotly({
  
  fig <- plot_ly(ThoraxRotRightNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Angle (deg)"))
  
  
  fig
  
#})

###NORMALISE THORAX LEFT ORIENTATION DATA AND PLOT #############

ThoraxRotLeftNorm = NULL
for (i in 1:length(ThoraxRotLeft)){
  xvalues = 1:length(ThoraxRotLeft[[i]])
  yvalues = ThoraxRotLeft[[i]]
  output_x_vals <- seq(1,length(xvalues),length.out=101)
  #
  # compute the interpolated values; this would be done for each input time series
  #
  #interp_output[[,i]]<- 
  
  ThoraxRotLeftNorm[[i]] <- approx(x=xvalues, y=yvalues, xout=output_x_vals)$y
}

ThoraxRotLeftNormCombined = do.call(cbind, ThoraxRotLeftNorm)
ThoraxRotLeftNormMean = rowMeans(ThoraxRotLeftNormCombined)
ThoraxRotLeftNormSD = apply(ThoraxRotLeftNormCombined[,-1], 1, sd)
ThoraxRotLeftNormPEB = ThoraxRotLeftNormMean + ThoraxRotLeftNormSD
ThoraxRotLeftNormNEB = ThoraxRotLeftNormMean - ThoraxRotLeftNormSD

if (ThoraxRotLeftNormMean[1] < 0){
  sign = 1
}else{
  sign = -1
}

ThoraxRotLeftNormMean <- ThoraxRotLeftNormMean*sign
ThoraxRotLeftNormSD <-  ThoraxRotLeftNormSD*sign
ThoraxRotLeftNormPEB <-  ThoraxRotLeftNormPEB*sign
ThoraxRotLeftNormNEB <-  ThoraxRotLeftNormNEB*sign

ThoraxRotLeftNormCombined2 = (as.data.frame(ThoraxRotLeftNormCombined))*sign
ThoraxRotLeftNormCombined2$perc = c(0:100)
ThoraxRotLeftNormCombined2 <- melt(ThoraxRotLeftNormCombined2, id.vars="perc")

ThoraxRotLeftNormMeanMax <- round(max(ThoraxRotLeftNormMean),2)
ThoraxRotLeftNormMeanMaxPC <- which.max(ThoraxRotLeftNormMean) -1   


# ggplot(ThoraxRotLeftNormCombined2) + geom_line(aes(perc,value, colour = variable))+ theme(legend.position = "none")+
#   scale_y_reverse()
# 
# 
# ggplot(ThoraxRotLeftNormMeanSD) + geom_line(aes(c(0:100),ThoraxRotLeftNormMean))+ geom_line(aes(c(0:100),ThoraxRotLeftNormPEB), linetype = "dashed")+ geom_line(aes(c(0:100),ThoraxRotLeftNormNEB),linetype = "dashed")+
#   scale_y_reverse()

#output$ThoraxRotLeft<- renderPlotly({
  
  fig <- plot_ly(ThoraxRotLeftNormCombined2, x = ~perc, y = ~value, showlegend = FALSE) %>% add_lines(color = ~ordered(variable))  %>% 
    layout(xaxis = list(title = "% of Stroke"), yaxis = list(title = "Rotation Angle (deg)"))
  
  fig
  
#})

#output$ThoraxRotCombined<- renderPlotly({
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = ThoraxRotRightNormMean, type = 'scatter', mode = 'lines',
              line = list(color = 'rgba(250, 0, 0, 1)'),
              showlegend = TRUE, name = 'Right Stroke Thorax Rotation')%>% 
    add_trace(y = ThoraxRotRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 10, 10, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'green'),
              showlegend = TRUE, name = 'Left Stroke Thorax Rotation')%>% 
    add_trace(y = ThoraxRotLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(0,100,80,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Angle (deg)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    legend = list(x = 0.5, y = 0.2)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
  
  
  
  
#})

```

Plot all the means together for the right side.

```{r, include=FALSE,message=FALSE}
#output$RotSequenceRight<- renderPlotly({
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = BoatAccRightNormMean*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              line = list(color = 'black',dash = 'dot'),
              showlegend = TRUE, name = 'Boat Acceleration')%>% 
    add_trace(y = BoatAccRightNormPEB*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccRightNormNEB*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityRightNormMean, type = 'scatter', mode = 'lines',yaxis = "y2",
              line = list(color = 'rgba(122, 39, 160, 1)',dash = 'dot'),
              showlegend = TRUE, name = 'Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityRightNormPEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160, 0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityRightNormNEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotRightNormMean, type = 'scatter', mode = 'lines', line = list(color = 'rgba(21, 0, 250, 1)'),
              showlegend = TRUE, name = 'Thorax Rotation')%>% 
    add_trace(y = ThoraxRotRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotRightNormMean, type = 'scatter', mode = 'lines',line = list(color = 'rgba(255, 117, 31,1)'),
              showlegend = TRUE, name = 'Pelvis Rotation')%>% 
    add_trace(y = PelvisRotRightNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotRightNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Angle (deg)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE,
                                 range = c(-40,40)),
                    yaxis2 = list(title = "Velocity (m/s)",
                                  overlaying = "y",
                                  side = "right",
                                  showgrid = FALSE,
                                  showline = FALSE,
                                  showticklabels = TRUE,
                                  ticks = 'outside',
                                  zeroline = TRUE,
                                  range = c(3,4),
                                  color = 'rgba(122, 39, 160, 1)'),
                    margin = list(l = 0, r = 50, b = 0, t = 0),
                    legend = list(orientation = 'h', x =0, y = -0.2)) %>%
    config(displayModeBar = F)
  
```

```{r,message=FALSE}
  fig
  
  
  
  
#})

```

And the left side.

```{r, include=FALSE,message=FALSE}

#output$RotSequenceLeft<- renderPlotly({
  
  fig <- plot_ly(x = c(0:100)) %>%
    add_trace(y = BoatAccLeftNormMean*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              line = list(color = 'black',dash = 'dot'),
              showlegend = TRUE, name = 'Boat Acceleration')%>% 
    add_trace(y = BoatAccLeftNormPEB*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = BoatAccLeftNormNEB*10, type = 'scatter', mode = 'lines',#yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(0,0,0,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormMean, type = 'scatter', mode = 'lines',yaxis = "y2",
              line = list(color = 'rgba(122, 39, 160, 1)',dash = 'dot'),
              showlegend = TRUE, name = 'Minimax Velocity')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormPEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160, 0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = MinimaxdfVelocityLeftNormNEB, type = 'scatter', mode = 'lines',yaxis = "y2",
              fill = 'tonexty', fillcolor='rgba(122, 39, 160,0.1)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotLeftNormMean, type = 'scatter', mode = 'lines', line = list(color = 'rgba(21, 0, 250, 1)'),
              showlegend = TRUE, name = 'Thorax Rotation')%>% 
    add_trace(y = ThoraxRotLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = ThoraxRotLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(21, 0, 250, 0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotLeftNormMean, type = 'scatter', mode = 'lines',line = list(color = 'rgba(255, 117, 31,1)'),
              showlegend = TRUE, name = 'Pelvis Rotation')%>% 
    add_trace(y = PelvisRotLeftNormPEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    add_trace(y = PelvisRotLeftNormNEB, type = 'scatter', mode = 'lines',
              fill = 'tonexty', fillcolor='rgba(255, 117, 31,0.2)', line = list(color = 'rgba(0,0,0,0)'),
              showlegend = FALSE, name = 'Lowerlimit')%>% 
    layout(         xaxis = list(title = "% of Stroke",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE),
                    yaxis = list(title = "Rotation Angle (deg)",
                                 showgrid = TRUE,
                                 showline = FALSE,
                                 showticklabels = TRUE,
                                 ticks = 'outside',
                                 zeroline = TRUE,
                                 range = c(-40,40)),
                    yaxis2 = list(title = "Velocity (m/s)",
                                  overlaying = "y",
                                  side = "right",
                                  showgrid = FALSE,
                                  showline = FALSE,
                                  showticklabels = TRUE,
                                  ticks = 'outside',
                                  zeroline = TRUE,
                                  range = c(3,4),
                                  color = 'rgba(122, 39, 160, 1)'),
                    margin = list(l = 0, r = 50, b = 0, t = 0),
                    legend = list(orientation = 'h', x =0, y = -0.2)) %>%
    config(displayModeBar = F)
  
```
```{r,message=FALSE}
  fig
#})
  
```

And collate the means into a datatable.

```{r, include=FALSE,message=FALSE}
SequenceAngledataRight <- data.frame(MinimaxdfVelocityRightNormMeanMax, MinimaxdfVelocityRightNormMeanMaxPC, PelvisRotRightNormMeanMax,  PelvisRotRightNormMeanMaxPC, ThoraxRotRightNormMeanMax, ThoraxRotRightNormMeanMaxPC)
colnames(SequenceAngledataRight) <- c("Minimax Velocity Max (m/s)", "%", "Pelvis Rotation Angle Max (deg)",  "%", "Thorax Rotation Angle Max (deg)", "%")
SequenceAngledataLeft <- data.frame(MinimaxdfVelocityLeftNormMeanMax, MinimaxdfVelocityLeftNormMeanMaxPC, PelvisRotLeftNormMeanMax,  PelvisRotLeftNormMeanMaxPC, ThoraxRotLeftNormMeanMax, ThoraxRotLeftNormMeanMaxPC)
colnames(SequenceAngledataLeft) <- c("Minimax Velocity Max (m/s)", "%", "Pelvis Rotation Angle Max (deg)",  "%", "Thorax Rotation Angle Max (deg)", "%")

SequenceAngledata <- rbind(SequenceAngledataRight,SequenceAngledataLeft)



#output$table_AngleSequence <- renderDataTable({ 
  
```
```{r,message=FALSE}
  datatable(SequenceAngledata,  rownames = c("Right", "Left"), options = list(columnDefs = list(list(className = 'dt-center', targets = "_all")),dom='t', ordering=F))%>% formatStyle(
    columns = c(3,4),
    #c('250m splits (secs)', "Race 2", "Avg Velocity (m/s)", "Avg Prog Speed (%)"),
    valueColumns = 0,
    target = 'cell',
    backgroundColor = 'rgba(112, 165, 255, 1)')
#})


```
